***Integration of environmental conditions***

# Integration with environmental data

We imported data from the [AHDB 2014 trials](https://cereals.ahdb.org.uk/varieties/current-trials-and-harvest-results/archive/rl-trials-and-harvest-results-2014/winter-wheat-trials-and-harvest-results-2014.aspx). We have yield for each variety and each location (publicly available). We also have the exact co-ordinates of the trial sites (provided by Bastiaan).

```{r}
wheat_yield <- read_csv('../Desktop/EBI hackaton/03102014 WW Yield Results.csv')
str(wheat_yield)

trial_id <- read_csv('../Desktop/EBI hackaton/TR_IDs.csv')

site_coords <- read_csv('../Desktop/EBI hackaton/AHDB RL data depository - Team 3 - WW2014 trial locations.csv')
str(site_coords)
```

We combined the two datasets containing the trial ID geographical coordinates and name of the trial site to get the exact location of the fields.

```{r}
site_coords_plus_ids <- right_join(site_coords,trial_id)
write_csv(site_coords_plus_ids, '../Desktop/EBI hackaton/site_coords_id.csv')
```

We then used the field coordinates to query the Agrimetrics API and obtain an Agrimetrics field ID for each site. We could retrieve the data but unfortunately only Field Trends for the 2015-2018 period are available (ie not our year of interest). We do not have the expertise to know how to make inferences out of this climate data, but we think it would ultimately help uncover varieties which perform better under specific environmental conditions.

